### 2012-10-14 3.tex
Checking on glosses

\begin{example}[The Turkish nominative]
\label{turknom}
\begin{tabular}{lllll}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & {ip}           & {ipler}    & `rope'         & \citep[][216]{Clements1982} \\
%  & {el}           & {eller}    & `hand'         \\
   & {köy}          & {köyler}   & `village'      \\
   & {yüz}          & {yüzler}   & `face'         \\
   & {kız}          & {kızlar}   & `girl'         \\
%  & {sap}          & {saplar}   & `stalk'        \\
%  & {son}          & {sonlar}   & `end'          \\
   & {pul}          & {pullar}   & `stamp'        \\
b. & {neden}        & {nedenler} & `reason'       & \citep{TELL} \\
   & {kiler}        & {kilerler} & `pantry'       \\
   & {pelür}        & {pelürler} & `tissue paper' \\
   & {boğaz}        & {boğazlar} & `throat'       \\
   & {sapık}        & {sapıklar} & `pervert'      \\
\end{tabular}
\end{example}

@@

\begin{example}[Exceptional Turkish nominatives] 
\label{turkexcept}
\begin{tabular}{lllll}
   & \emph{nom.sg.} & \emph{nom.pl.}             &                    \\
a. & {mezar}        & {mezarlar} & `grave'       & \citep{TELL}       \\
   & {model}        & {modeller} & `model'                            \\
   & {silah}        & {silahlar} & `weapon'                           \\
   & {memur}        & {memurlar} & `bureaucrat'                       \\
   & {sabun}        & {sabunlar} & `soap'                             \\
b. & {etol}         & {etoller}  & `fur stole'   & \citep{Goksel2005} \\
   & {saat}         & {saatler}  & `hour, clock' 	                  \\
%  & {harf}         & {harfler}  & `(alphabetic) letter' \\ 
\end{tabular}
\end{example}

\noindent
There is also a very small class of nouns, shown in (\ref{turkexcept}b), which take \emph{-ler} despite the fact that their final root vowel is [$+$\textsc{Back}]. While suffix disharmony appears to very sporadic, the co-occurrence of suffix harmony and root disharmony has been the subject of much debate. As disharmonic roots still trigger suffix harmony, 
%\citet[212, 289]{Anderson1974} and
\citet{Iverson1978} distinguish suffix harmony alternations from the sequence structure constraint governing root harmony.\footnote{\citet[29f.]{Kiparsky1968} discusses a parallel case in Finnish, and proposes a similar separation between the exception-filled sequence structure constraint and an exceptionless suffix harmony process. \citet[171f.]{Howard1972} correctly observes that this duplication is unnecessary.}

@@

\begin{example}[Variable non-native cluster adaptation (\citealp{Clements1982}:247)] 
\begin{tabular}{lllll}
a. & {spiker}  & \alt{} & {sipiker}  & `announcer' \\
   & {fren}    & \alt{} & {firen}    & `break'     \\
b. & {trablus} & \alt{} & {tırablus} & `Tripoli'   \\
   & {kral}    & \alt{} & {kıral}    & `king'      \\
c. & {brom}    & \alt{} & {burom}    & `bromide'   \\
   & {prusya}  & \alt{} & {purusya}  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
\end{tabular}
\end{example}

@@

\begin{example}[Turkish nominal suffix allomorphy]
\begin{tabular}{lllllll}
   & \emph{nom.sg.} & \emph{dat.sg.} & \emph{gen.sg.}  \\
a. & {ip}           & {ipi}          & {ipin}         & `rope' & \citep[][216]{Clements1982} \\
%  & {el}           & {eli}          & {elin}         & `hand'    \\
   & {kız}          & {kızı}         & {kızın}        & `girl'    \\
   & {sap}          & {sapı}         & {sapın}        & `stalk'   \\
%  & {yüz}          & {yüzü}         & {yüzün}        & `face'    \\
   & {köy}          & {köyü}         & {köyün}        & `village' \\
%  & {pul}          & {pulu}         & {pulun}        & `stamp'   \\
   & {son}          & {sonu}         & {sonun}        & `end'     \\
b. & {boğaz}        & {boğazı}       & {boğazın}      & `throat'  & \citep{TELL} \\
   & {pelür}        & {pelürü}       & {pelürün}      & `tissue' \\
   & {döviz}        & {dövizi}       & {dövizin}      & `currency' \\
   & {yamuk}        & {yamuğu}       & {yamuğun}      & `trapezoid' \\
   & {ümit}         & {ümiti}        & {ümitin}       & `hope'     \\
\end{tabular}
\end{example}

@@

\citet{NiChiosain1993} and \citet{Ito1995b} argue that \textsc{Labial Attraction} is true only of native vocabulary. This would be a potential confound for the experimental results, since it is not implausible that the subjects' in \citeauthor{Zimmer1969}'s study treated nonce words as if they were loanwords.\footnote{Indeed, many wordlikeness studies include instructions to the participants to treat the stimuli much as if they were loanwords \citep[e.g.,][]{Hay2004a}. This may influence the choice of task model used by participants.} However, this was not the opinion of \citet[266]{Lees1966a}, and is conclusively refuted by  \citet{Inkelas2001}. They observe that in the subset of the TELL database with etymological coding, a full 75\% of foreign vocabulary conform to \textsc{Labial Attraction}, which is surprisingly a smaller percentage than that of the foreign vocabulary (52\%), a significant trend (Fisher exact test, $p = 0.042$). One plausible explanation is that many of the languages in contact with Turkish lack the \emph{ı} phoneme needed to violate \textsc{Labial Attraction}.

@@

%It is difficult to evaluate their claim in the absense of a theory of phonotactic naturalness, something which has consisteny eluded formalization for decades. Even the informal definition used by \citeauthor{Becker2011} is flawed. \citeauthor{Becker2011} label generalizations unnatural if they lack phonetic precursors, or if they are not unattested---no description of the methodology used to determine attestedness is given. These two varieties of evidence are not fully independent, however: extragrammatical \emph{channel bias} effects are thought to be a first-order predictor of attestation \citep{Blevins2004,Moreton2008}. In light of extensive evidence for generalizations which are phonetically unnatural \citep[e.g.,]{Anderson1981,Bach1972,Buckley2000a}, even as revealed in nonce word studies \citep[e.g.,][]{Hayes2009}, the fact that the generalizations extracted in the \citet{Becker2011} study are phonetically natural is either accident or conundrum. It is certainly not something that can be explained by the tacit theory of possible gneeralizations the authors adhere to.

>>>>

\begin{example}[The Turkish nominative]
\label{turknom}
\begin{tabular}{lllll}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & {ip}           & {ipler}    & `rope'         & \citep[][216]{Clements1982} \\
%  & {el}           & {eller}    & `hand'         \\
   & {köy}          & {köyler}   & `village'      \\
   & {yüz}          & {yüzler}   & `face'         \\
   & {kız}          & {kızlar}   & `girl'         \\
%  & {sap}          & {saplar}   & `stalk'        \\
%  & {son}          & {sonlar}   & `end'          \\
   & {pul}          & {pullar}   & `stamp'        \\
b. & {neden}        & {nedenler} & `reason'       & \citep{TELL} \\
   & {kiler}        & {kilerler} & `pantry'       \\
   & {pelür}        & {pelürler} & `onionskin'    \\
   & {boğaz}        & {boğazlar} & `throat'       \\
   & {sapık}        & {sapıklar} & `pervert'      \\
\end{tabular}
\end{example}

@@

\begin{example}[Exceptional Turkish nominatives] 
\label{turkexcept}
\begin{tabular}{lllll}
   & \emph{nom.sg.} & \emph{nom.pl.}             &                    \\
a. & {mezar}        & {mezarlar} & `grave'       & \citep{TELL}       \\
   & {model}        & {modeller} & `model'                            \\
   & {silah}        & {silahlar} & `weapon'                           \\
   & {memur}        & {memurlar} & `official'                         \\
   & {sabun}        & {sabunlar} & `soap'                             \\
b. & {etol}         & {etoller}  & `fur stole'   & \citep{Goksel2005} \\
   & {saat}         & {saatler}  & `hour, clock' 	                  \\
%  & {harf}         & {harfler}  & `(alphabetic) letter' \\ 
\end{tabular}
\end{example}

\noindent
There is also a very small class of nouns, shown in (\ref{turkexcept}b), which take \emph{-ler} though their final root vowel is [$+$\textsc{Back}]. While suffix disharmony appears to very sporadic, the co-occurrence of suffix harmony and root disharmony has been the subject of much debate. As disharmonic roots still trigger suffix harmony, 
%\citet[212, 289]{Anderson1974} and
\citet{Iverson1978} distinguish suffix harmony alternations from the sequence structure constraint governing root harmony.\footnote{\citet[29f.]{Kiparsky1968} discusses a parallel case in Finnish, and proposes a similar separation between the exception-filled sequence structure constraint and an exceptionless suffix harmony process. \citet[171f.]{Howard1972} correctly observes that this duplication is unnecessary.}

@@

\begin{example}[Variable non-native cluster adaptation (\citealp{Clements1982}:247)] 
\begin{tabular}{lllll}
a. & {spiker}  & \alt{} & {sipiker}  & `announcer' \\
   & {fren}    & \alt{} & {firen}    & `brake'     \\
b. & {trablus} & \alt{} & {tırablus} & `Tripoli'   \\
   & {kral}    & \alt{} & {kıral}    & `king'      \\
c. & {brom}    & \alt{} & {burom}    & `bromide'   \\
   & {prusya}  & \alt{} & {purusya}  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
\end{tabular}
\end{example}

@@

\begin{example}[Turkish nominal suffix allomorphy]
\begin{tabular}{lllllll}
   & \emph{nom.sg.} & \emph{dat.sg.} & \emph{gen.sg.}  \\
a. & {ip}           & {ipi}          & {ipin}         & `rope' & \citep[][216]{Clements1982} \\
%  & {el}           & {eli}          & {elin}         & `hand'    \\
   & {kız}          & {kızı}         & {kızın}        & `girl'    \\
   & {sap}          & {sapı}         & {sapın}        & `stalk'  \\
%  & {yüz}          & {yüzü}         & {yüzün}        & `face'    \\
   & {köy}          & {köyü}         & {köyün}        & `village' \\
%  & {pul}          & {pulu}         & {pulun}        & `stamp'   \\
   & {son}          & {sonu}         & {sonun}        & `end'     \\
b. & {boğaz}        & {boğazı}       & {boğazın}      & `throat'  & \citep{TELL} \\
   & {pelür}        & {pelürü}       & {pelürün}      & `onionskin' \\
   & {döviz}        & {dövizi}       & {dövizin}      & `currency'  \\
   & {yamuk}        & {yamuğu}       & {yamuğun}      & `trapezoid' \\
   & {ümit}         & {ümiti}        & {ümitin}       & `hope'      \\
\end{tabular}
\end{example}

@@

\citet{NiChiosain1993} and \citet{Ito1995b} argue that \textsc{Labial Attraction} is true only of native vocabulary. This would be a potential confound for the experimental results, since it is not implausible that the subjects' in \citeauthor{Zimmer1969}'s study treated nonce words as if they were loanwords. 
%\footnote{Indeed, many wordlikeness studies include instructions to the participants to treat the stimuli much as if they were loanwords \citep[e.g.,][]{Hay2004a}. This may influence the choice of task model used by participants.}
This was not the opinion of \citet[266]{Lees1966a}, and it is conclusively refuted by  \citet{Inkelas2001}. They observe that in the subset of the TELL database with etymological coding, a full 75\% of foreign vocabulary conform to \textsc{Labial Attraction}, which is surprisingly a smaller percentage than that of the foreign vocabulary (52\%), a significant trend (Fisher exact test, $p = 0.042$). One plausible explanation is that many of the languages in contact with Turkish lack the \emph{ı} phoneme needed to violate \textsc{Labial Attraction}.

@@

%It is difficult to evaluate their claim in the absense of a theory of phonotactic naturalness, something which has consisteny eluded formalization for decades. Even the informal definition used by \citeauthor{Becker2011} is flawed. \citeauthor{Becker2011} label generalizations unnatural if they lack phonetic precursors, or if they are not unattested---no description of the methodology used to determine attestedness is given. These two varieties of evidence are not fully independent, however: extragrammatical \emph{channel bias} effects are thought to be a first-order predictor of attestation \citep{Blevins2004,Moreton2008}. In light of extensive evidence for generalizations which are phonetically unnatural \citep[e.g.,]{Anderson1981,Bach1972,Buckley2000a}, even as revealed in nonce word studies \citep[e.g.,][]{Hayes2009}, the generalizations extracted in the \citet{Becker2011} study are phonetically natural is either accident or conundrum. It is certainly not something that can be explained by the tacit theory of possible gneeralizations the authors adhere to.
